\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2015-01-08 proposal/sections/implication-risk.tex
Costs

\section{Expected implications and risks}
\label{sect:implication-risk}

@@

\subsubsection*{Less money}
\begin{itemize}
 \item Description: Get less money to realize the project than defined in the cost accounting.
 \item Solution: Our project is calculated tightly. So we must revalidate the hole project and create a new proposal with less features and workpackages.
\end{itemize}

\subsubsection*{More money needed}
\begin{itemize}
 \item Description: The project needs more money than defined in the cost accounting.
 \item Solution: Looking for new investors to get more money. Sell knowhow to other companies or research groups.
\end{itemize}

\subsubsection*{Less time for research}
\begin{itemize}
 \item Description: The brain waves research needs more time than supposed.
 \item Solution: Buy knowhow from other companies and research groups. Get extern experts to increase the research.
\end{itemize}

\subsubsection*{Team members leave}
\begin{itemize}
 \item Description: One or more team members leave the project.
 \item Solution: All work topics have two members. To avoid loosing knowlegde, there are meetings every week to beware it. After knowlegde about leaving a team member, we are looking for a new team member.
\end{itemize}

@@

\subsubsection*{Missinterpretion}
\begin{itemize}
 \item Description: The team members not understand the specification correctly.
 \item Solution: Make meetings and reviews to ensure that every team member has understand it correctly.
\end{itemize}

>>>>

\section{Expected Implications and Risks}
\label{sect:implication-risk}

@@

\subsubsection*{Less money}
\begin{itemize}
 \item Description: Get less money to realize the project than defined in the cost accounting.
 \item Solution: Our project is calculated tightly. So we must revalidate the hole project and create a new proposal with less features and work packages.
\end{itemize}

\subsubsection*{More money needed}
\begin{itemize}
 \item Description: The project needs more money than defined in the cost accounting.
 \item Solution: Looking for new investors to get more money. Sell know-how to other companies or research groups.
\end{itemize}

\subsubsection*{Less time for research}
\begin{itemize}
 \item Description: The brain waves research needs more time than supposed.
 \item Solution: Buy know-how from other companies and research groups. Get external experts to increase the research.
\end{itemize}

\subsubsection*{Team members leave}
\begin{itemize}
 \item Description: One or more team members leave the project.
 \item Solution: All work topics have two members. To avoid loosing knowledge, there are meetings every week to beware it. After knowledge about leaving a team member, we are looking for a new team member.
\end{itemize}

@@

\subsubsection*{Misinterpretation}
\begin{itemize}
 \item Description: The team members not understand the specification correctly.
 \item Solution: Make meetings and reviews to ensure that every team member has understand it correctly.
\end{itemize}
